Multiphysics Reactor-core Simulations Using the Improved Quasi-Static Method

### 2018-04-05 doc/Papers/IQS_convergence/IQS_convergence.tex
final review and sdirk33 ref

Solving for the shape in \eqt{eq:shape} can become expensive, especially in two or three spatial dimensions, and even more so when using 
the transport equations in lieu of the diffusion equations.  Using IQS, one expects the time dependence of the shape to be weaker than that 
of the flux itself, thus allowing for larger time step sizes in updating the shape. The PRKE equations form a small ODE system and can be 
solved using a much smaller time step size. In transients where the shape varies much less than the flux, IQS can be very computationally effective. 
%The two-time scale solution process, a micro scale for the PRKE and a macro scale for the shape, is illustrated in \fig{fig:iqsviz}.  
%\begin{figure}[!htbp]
%\centering
%\includegraphics[width=\linewidth]{figures/IQS_visualization.jpg}
%\caption{IQS method visualization}
%\label{fig:iqsviz}
%\end{figure}
%
Note that the PRKE parameters are evaluated at each macro step and interpolated for the PRKE evaluation. In order to preserve 
the error convergence rate of high order temporal discretization schemes for shape, higher order interpolation of the parameters will be required. Third order implicit Runge-Kutta discretization with time step adaptation was used for the PRKE evaluation, to insure a negligibly small error in the amplitude solution.

@@

The LRA benchmark is a two-dimensional, two-group neutron diffusion problem.  
It is a super prompt-critical transient. The execution of the benchmark was performed by the Rattlesnake/MOOSE framework at Idaho National Laboratory (INL) \cite{wang2013}.  The spatial discretization uses continuous finite elements with first-order Lagrangian basis functions. The mesh consists of blocks $11\times 11$ with five uniform refinements, totaling $165,165$ elements and $124,609$ nodes. Three different temporal solution techniques are used: implicit discretization of the flux equations, IQS formulation, and \iqspc. Crank-Nicolson time discretization scheme is used for the space-time equations. \jcr{when you recall all common numerical options, make sure you recall that the PRKE ODE are done with high-order implicit RK. Put all info that is common to all results in 1 location at the beginning}. 
\zmp{I put the PRKE evaluation detail in the theory section. Should I put it again here?}
The performance of IQS with temperature feedback is assessed by comparing the solution accuracy at peak power.

@@

>>>>

Solving for the shape in \eqt{eq:shape} can become expensive, especially in two or three spatial dimensions, and even more so when using 
the transport equations in lieu of the diffusion equations.  Using IQS, one expects the time dependence of the shape to be weaker than that 
of the flux itself, thus allowing for larger time step sizes in updating the shape. The PRKE equations form a small ODE system and can be 
solved using a much smaller time step size. In transients where the shape varies much less than the flux, IQS can be very computationally effective. 
%The two-time scale solution process, a micro scale for the PRKE and a macro scale for the shape, is illustrated in \fig{fig:iqsviz}.  
%\begin{figure}[!htbp]
%\centering
%\includegraphics[width=\linewidth]{figures/IQS_visualization.jpg}
%\caption{IQS method visualization}
%\label{fig:iqsviz}
%\end{figure}
%
Note that the PRKE parameters are evaluated at each macro step and interpolated for the PRKE evaluation. In order to preserve 
the error convergence rate of high order temporal discretization schemes for shape, higher order interpolation of the parameters is required. A third-order implicit Runge-Kutta \cite{sdirk33} discretization with time-step adaptation is used for all PRKE evaluations in this paper in 
order to ensure a negligibly small error in the amplitude solution.

@@

The LRA benchmark is a two-dimensional, two-group neutron diffusion problem.  
It is a super prompt-critical transient. The execution of the benchmark was performed by the Rattlesnake/MOOSE framework at Idaho National Laboratory (INL) \cite{wang2013}.  The spatial discretization uses continuous finite elements with first-order Lagrangian basis functions. The mesh consists of blocks $11\times 11$ with five uniform refinements, totaling $165,165$ elements and $124,609$ nodes. Three different temporal solution techniques are used: implicit discretization of the flux equations, IQS formulation, and \iqspc. Crank-Nicolson time discretization scheme is used for the space-time equations. 
The performance of IQS with temperature feedback is assessed by comparing the solution accuracy at peak power.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This work was supported by the Department of Energy through grant DE-AC07-05ID14517 (Idaho National Laboratory) and the Integrated University Program Fellowship (Cooperative Agreement DE-NE0000112).  We thank Mark D. Dehart, Yaqi Wang, and INL's MOOSE/Rattlesnake team for their support.
